Mysterious radio flashes could trace Universe's largest structures

### 2015-08-20 writeup/summary.tex
merged summaries.

\title{Mysterious radio flashes to be used to trace Universe's largest
structures}

@@

One of the most challenging aspects of astronomy is determining distances to
far-off objects. Newly discovered fast radio bursts---thought to originate from
the far reaches of the Universe---provide distance measurements that will
enable the largest structures of the cosmos to be studied in three dimensions.
Traditionally cosmological distances are obtained using Doppler shifts, caused
by the Hubble expansion of the Universe. In contrast, distortions to fast radio
burst signals can be used to measure the total amount material between earth
and the burst's source, permitting another way to determine distance.  However
this process isn't perfect, as intervening clumps of excess matter can distort the
measured distance. This fact can be exploited to glean yet more
information through these intervening structures.  Wide-field radio telescopes
are expecting to detect thousands of these bursts, opening a new window for
studying the cosmos.

>>>>

\title{Mysterious radio flashes could trace Universe's largest
structures}

@@

One of the most challenging aspects of astronomy is determining distances to
far-off objects. Newly discovered fast radio bursts---thought to originate from
the far reaches of the Universe---provide distance measurements that may
enable the largest structures of the cosmos to be studied in three dimensions.
Cosmological distances are traditionally determined using Doppler shifts, caused
by the Hubble expansion of the Universe. In contrast, delays to fast radio
burst signals can be used to tally the total amount of material between earth
and the burst's source, permitting another way to determine distance.
As intervening clumps of cosmic matter can add extra delay, these
measured distances don't exactly match the actual distances.
However, these distortions reveal information about the intervening
structure.
Wide-field radio telescopes could detect thousands of these bursts, opening a
new window for studying the cosmos.
